\section{Introduction And Motivation}
The study of how light interacts with matter at extremely high-intensity levels, known as Ultra High Light Intensity (UHLI), has garnered significant interest.  The main objective is to achieve high-intensity levels, such as the experimental attainment of laser intensities of around $10^{23} W/cm^{-2}$ using the CoReLS petawatt (PW) laser\cite{highintensity}, which can provide access to novel physical regimes. At these ultra-high intensities, laser-plasma interactions lead to various nonlinear processes, including the widely studied high harmonic generation\cite{henri}. High harmonics have various applications, such as ultrafast quantum information processing, attosecond sources, and all-optical mapping of the electronic band structure. One method of generating high harmonics involves using plasma, which is discussed in this article.

When a laser pulse is incident upon plasma, it reflects if the density of plasma is high, forming PM. Upon reflection from plasma the laser field, because of pondermotive force, propels a relativistic oscillation of the PM which results in periodic temporal compression of the reflected field. These oscillations result in the generation of high harmonics of the incident laser frequency.\cite{lichters} Experimental demonstrations have shown the generation of high harmonics up to the 141st order of Nd glass laser\cite{hormonics1}, 109th order of Ti sapphire laser\cite{hormonics2}, and 37th order of krypton fluoride laser\cite{hormonics3}.

To begin, a concise explanation of high harmonic generation is provided, including its occurrence in both gases\cite{gas-main}\cite{gas-second}\cite{hhg-book} and plasma\cite{hhg-relativistic}\cite{hhg-main}\cite{hhg-second}\cite{history-similarity}\cite{universal-spectra}. The focus then shifts to the generation of harmonics of an incident laser pulse through interaction with an overdense plasma layer at a step boundary, under the influence of a high-intensity laser pulse. The impact of the laser pulse envelope, super-Gaussian (SG) with different rank $p$, on the resulting high harmonics is explored. Previously, simulations involving normal laser incidence revealed that only odd harmonics were generated. However, in the present report, various polarization and oblique incidences of laser light are simulated, resulting in the generation of both odd and even harmonics. For this, fully relativistic particle-in-cell simulations are performed using \textit{EPOCH}\cite{EPOCH}.