\hypertarget{high-harmonic-in-gases}{%
\section{High Harmonic in Gases}\label{high-harmonic-in-gases}}

High harmonic in gases occurs when an intense laser pulse is focused on
gases. When a light photon is interact with atom of gases, then their is
3 type of ionization depending on the frequency and intensity of the
light, if the energy of photon is greater or just equal to the atom
ionization potential, then photon ionization is occurs. in case if
energy of laser is lss than the atom ionization potential then
multiphoton ionization and tunneling ionization occur.

Multiphoton and tunneling ionization are two limiting cases of the
universal process of nonlinear ionization and this process is determined
by three parameters --- the laser frequency \(\omega\) , the amplitude
of the laser field strength F, and the atomic ionization potential
\(E_i\)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Multiphoton ionization: In the multiphoton limit the ionization rate
  depends on the field strength according to the power law:
  \[\omega = F^{2K}\] where K = \textless{}\(E_i\)/\(\omega\)
  +1\textgreater{} is the number of absorbed photons
\item
  In the tunneling limit the ionization rate increases exponentially
  with the field strength \[\omega \propto  \exp(-2(2E_i)^{3/2}/3F)\]
\end{enumerate}

it was shown that the boundary between multiphoton and tunneling
ionization is determined by the value of the so called adiabaticity
parameter: \[ \gamma =\omega \sqrt{2E_i/F}\] if \(\gamma^{2}>>1\)
correspond to multiphoton ionization; this process is realized at a
relatively high frequency and low field strength of laser radiation.
Oppositely, the values of \(\gamma^{2}<<1\) correspond to tunneling
ionization, which is realized at a low frequency and high field
strength.

\hypertarget{three-step-model}{%
\subsection{Three Step Model}\label{three-step-model}}

In the three-step model, the HHG process is decomposed as follows: (1)
tunnel ionization (2) free propagation in the presence of the field, and
(3) recollision and recombination producing HHG emission.

According to this model the electron is initially treated quantum
mechanically as it tunnel ionizes from the parent atom but then its
subsequent dynamics are treated classically. The electron is assumed to
be born into the vacuum with zero initial velocity, and to be
subsequently accelerated by the laser beam's electric field. Half an
optical cycle after ionization, the electron will reverse direction as
the electric field changes, and will accelerate back towards the parent
nucleus and collide with it.this is recombination process. during a
recombination process with the atom as it returns to its ground state,
it can emit radiation of many different frequency which is knows as high
harmonics in gases.

The solid blue line shows the potential created by the instantaneous
laser field and the binding potential well. The solid black line shows
the binding potential well on its own. red line shows the electron wave
function.

The laser field, which we have assumed to be linearly polarized along
the x axis which means that the electric field is
\(F(t) = -e_xFcos(\omega_L t)\) and the interaction with the laser field
is \(\hat V_L t=-dF(t) = -qxF(t)=-xFcos(\omega_Lt)\) in natural units
\(q=-1\). The minus in front of \(cos(\omega_Lt)\) means that the
elctron moves to the right when \(cos(\omega_Lt)>0\), just as shown in
figure.
